### 2017-12-01 Writing/draft.tex
Updated affiliations

\noindent {\normalsize \sc Thomas Guillerme$^1$$^*$, and Martin D. Brazeau$^1$}\\
\noindent {\small \it 
$^1$Imperial College London, Silwood Park Campus, Department of Life Sciences, Buckhurst Road, Ascot SL5 7PY, United Kingdom.\\}
\end{center}
\medskip
\noindent{*\bf Corresponding author.} \textit{guillert@tcd.ie}\\ 
\vspace{1in}

>>>>

\noindent {\normalsize \sc Thomas Guillerme$^1$$^2$$^*$, and Martin D. Brazeau$^2$$^3$}\\
\noindent {\small \it 
$^1$School of Biological Sciences, University of Queensland, St. Lucia, Queensland, Australia.\\
$^2$Imperial College London, Silwood Park Campus, Department of Life Sciences, Buckhurst Road, Ascot SL5 7PY, United Kingdom.\\
$^3$Department of Earth Sciences, Natural History Museum, Cromwell Road, London, SW75BD, United Kingdom.\\}

\end{center}
\medskip
\noindent{*\bf Corresponding author.} \textit{guillert@tcd.ie}\\ 
\vspace{1in}
